Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated slides (final version for Bocconi seminar)

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
\end{itemize_2pt}
\end{frame}

@@

		\item Example practices:

		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}

@@

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology boosting productivity factor $\textcolor{red}{A}$
			\item[] \citep[see,][]{Bloom2016, McKenzie2017, Quinn2019}
		\end{enumerate_2pt}

@@

Standard Production Decision
\begin{itemize_2pt}
	\item \tiny Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:

@@

	\item \normalsize Further specific channels of impact
	\begin{enumerate_2pt}
		\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
		\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013}
		\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

		\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
		\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
	\end{enumerate_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
	\item Correlation with productivity in mid-sized and large firms \citep{Bloom2019}
	\item \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms \citep{McKenzie2017}
	\end{itemize_2pt}

@@

	Open questions
	\begin{itemize_2pt}
		\item Does adoption of "best practices" \emph{cause} performance to increase?
		\item How can adoption of practices best be encouraged?
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_2pt}
	%\textcolor{}{}
	\item \textcolor{red}{Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	Demand for business training

@@

	\begin{itemize_2pt}
	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	Delivery 
	\begin{itemize_2pt}
	\item %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Performance}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Performance}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	Including more recent evaluations \citep[see,][]{McKenzie2021}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=21.5em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits}
	\end{figure}

@@

	\begin{itemize_2pt}
		\item Small positive impact on practice adoption, profits, and \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
	\end{itemize_2pt}

@@

		\item Training of skills in \textcolor{bdf}{particular domains}
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{specific constraints}
			\item Investigating mechanisms of treatment impact
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016, McKenziePuerto2021}
		\item ?
		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item
			\item
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item Marcel Fafchamps and Simon Quinn, \citep{McKenzie2017a}
	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Training Specific Domains}

	\citet{Anderson2018} assign 852 South African MSEs to distinct types of training:
	\begin{enumerate_2pt}
		\item Marketing/sales skills
		\item[]
		\item[]
		\item Finance/accounting skills
		\item[]
		\item[]
	\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Training Specific Domains}

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}

		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item 61\% increase in profits
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
		\end{itemize_2pt}

@@

		\begin{itemize_2pt}
			\item 41\% increase in profits
			\item "Efficiency focus" on lower costs
			\item[] $\rightarrow$ Benefits established businesses
		\end{itemize_2pt}

@@

Typical Consulting Intervention
\begin{itemize_2pt}
	\item Three-step procedure
	\begin{enumerate_2pt}
		\item Diagnosing practices
		\item Identifying areas of improvement
		\item Joint and interactive problem solving
	\end{enumerate_2pt}

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018, Karlan2015, Bruhn2019}
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

@@

@@

SME consulting \citep{Bruhn2018}
\begin{itemize_2pt}
	\item Evaluation of a matching grants program in Mexico
	\begin{itemize_2pt}
		\item
	\end{itemize_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_2pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_2pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	Text messages
	\begin{itemize_2pt}
	\item \citep{Cole2019} \citep{Acimovic2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_2pt}
	\item McKenzie cash JDE paper
	\item \citep{Gine2021}
	\item \cite{Berge2015}
	\item \cite{deMel2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_2pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}

@@

\begin{frame}
\frametitle{Self-reports and aggregation}

\citep{Garlick2019}
\citep{deMel2009}
\citep{Bernhardt2019}

@@

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Self-reports and aggregation}
	\begin{itemize_2pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_2pt}
	\item  \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_2pt}
	\item \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
Direct measurements
	\begin{itemize_2pt}
	\item \citep{Fafchamps2012} Personalized Digital Assistants (PDAs) for MSEs in Ghana
	\item[] $\rightarrow$ Vast majority of large changes in sales and profits genuine income volatility
	\end{itemize_2pt}
\end{frame}

% ---------------------

\begin{frame}
\frametitle{?}
\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{?}
\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

@@

	\item Some more obvious constraints (already mentioned in passing):
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Credit constraints} \citep[see, e.g.,][]{} McKenzie cash paper
		\item \textcolor{bdf}{Gender norms and constraints}
		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
	\end{itemize_2pt} 
\end{itemize_2pt}

@@

$\rightarrow$ More recent literature highlights \textcolor{bdf}{behavioral constraints}

@@

Potential for heuristics and rules of thumb
\begin{itemize_2pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

@@

Complementarities in skills
\begin{itemize_2pt}
	\item
\end{itemize_2pt}

@@

Learning styles
\begin{itemize_2pt}
	\item
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Family Commitments}
\begin{itemize_2pt}
	\item Interesting; \textcolor{red}{no beh const}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Segregated Markets}
\begin{itemize_2pt}
	\item Missing economies of scale
	\item \textcolor{red}{Interesting; not behavioral constraint}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

%\begin{frame}
%\frametitle{Identity Concerns}
%\begin{itemize_2pt}
%	\item 
%	\vspace{0.1in}
%\end{itemize_2pt}
%\end{frame}

\begin{frame}
\frametitle{Aspirations}
\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Business Practices}
\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

>>>>

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{(Bloom et al., 2007, Bloom et al., 2010, Syverson, 2011)}
\end{itemize_2pt}
\end{frame}

@@

@@

%\begin{frame}
%\frametitle{Characterization of Business Practices}

%\begin{itemize_2pt}
%	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance

%	\begin{itemize_2pt}	
%	\vspace{0.5em}

%		\item Example practices:

%		\begin{enumerate_2pt}
%			\item e.g., 
%			\item e.g., 
%			\item e.g., 
%			\item e.g.,  
%		\end{enumerate_2pt}

%		\vspace{0.5em}

%	\end{itemize_2pt}

%\end{itemize_2pt}

%\end{frame}

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology affecting productivity factor $\textcolor{red}{A}$
			\item[] See, e.g., \textcolor{camel}{Bloom et al., (2016), McKenzie and Woodruff (2017)} %Quinn2019}
		\end{enumerate_2pt}

@@

\begin{itemize_2pt}

	\item \normalsize Further specific channels of potential impact
	\begin{enumerate_2pt}
		\item Better \textcolor{bdf}{negotiation practices} may affect raw material prices $\textcolor{red}{s}$
		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend (see, e.g., \textcolor{camel}{Bruhn and Zia, 2013})
		\item \textcolor{bdf}{Marketing practices} may affect output price $\textcolor{red}{p}$ by changing demand

		\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth

@@

		\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
	\end{enumerate_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Business Practices and Performance}

	Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
	\begin{itemize_2pt}
		\item Robust correlation with productivity in \textcolor{bdf}{mid-sized and large firms}, and in the \textcolor{bdf}{public sector} \citep{Bloom2015,Bloom2020} %\citep{Bloom2019}
		\item Robust correlation with performance and firm survival across industries and contexts in \textcolor{bdf}{small firms} \citep{McKenzie2017}
		\end{itemize_2pt}

@@

	Open questions
	\begin{itemize_2pt}
		\item Does adoption of best practices \emph{cause} performance to increase?
		\item How can adoption of practices best be encouraged?
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Typical Training Program}
Stylized facts on MSME trainings
\begin{itemize_2pt}
	\item Group of 15 to 40 entrepreneurs per trainer
	\item In-class (often with elements of active and interactive learning)
	\item Period of up to two weeks	
	\item Foci of typical syllabi
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Encourage start-up}: Business ideas and business plans, permits, costing, pricing, and budgeting
		\item \textcolor{bdf}{Grow existing businesses}: Record-keeping, accounting, and financial planning, marketing, human resources and hiring, stock and inventory management
	\end{itemize_2pt}

	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{Lieshout2017})
	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
	\item[] \quad (Median contribution 10\% of full price)

\begin{frame}
\frametitle{Typical Training Program}

Demand for business training

@@

\begin{itemize_2pt}
	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Impact on Performance}
First wave of evaluations
	\begin{itemize_2pt}
	\item  Headline result: \textcolor{bdf}{No impact on business performance}
	\begin{itemize_2pt}
		\item Modest short-term adoption of practices (long-term fade-out)
		\item Null-effect on business sales and profits
		\item Early examples: \textcolor{camel}{Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010} 
		%\item Later examples: \textcolor{camel}{Bulte et al., 2017; Anderson, Chandy, and Zia, 2018}

	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Performance}

Econometric and implementation issues \citep{McKenzie2014}
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Lack of statistical power} with MDEs often substantially above policy-relevant levels
		\begin{itemize_2pt}	
			\item Small samples (typically $N=200-400$ per treatment cell)
			\item Typical attendance between 40 and 70\%
			\item Typically substantial rates of survey attrition (up to $24-28\%$)
			\item Large heterogeneity in age, education, training delivery and costs, etc.
		\end{itemize_2pt}

		\item Endline follow-ups \textcolor{bdf}{very short-term} (typically 1-2 years out)

		\item Sources of \textcolor{bdf}{selection bias} by treatment status
		\begin{itemize_2pt}	
			\item Firm survival can be endogenous on treatment
			\item Record-keeping likely to increase reporting accuracy
			\item Clear potential for differential experimenter demand effects
		\end{itemize_2pt}

		\item Most trainings offered at \textcolor{bdf}{no private costs}
		\begin{itemize_2pt}
			\item Potential for reverse sunken cost fallacy in valuation \citep[see,][]{Maffioli2020}
		\end{itemize_2pt}

		%\item Focus on \textcolor{bdf}{existing businesses} and \textcolor{bdf}{middle-aged entrepreneurs} (typical age 35 to 45 years)

@@

	Recent meta-study \citep{McKenzie2021}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=20em]{pics/McK2020_profits.png}
		\label{McKenzie(2020): Profits}
	\end{figure}

@@

	\begin{itemize_2pt}
		\item \textcolor{bdf}{Small positive impact} on practice adoption and performance 
		\item[] $\rightarrow$ Estimated 10.1\% plus in profits, and 4.7\% plus in \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
	\end{itemize_2pt}

@@

		\item Training of \textcolor{bdf}{specific clusters of business practices}
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{specific constraints}
			\item Investigating mechanisms of treatment impact
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item Examples: 
		\begin{itemize_2pt}
			\item Gender and Enterprise Together (GET Ahead, ILO; \textcolor{camel}{Bulte et al., 2017}, \textcolor{camel}{McKenzie and Puerto, 2021})
			\item Start and Improve Your Business (SIYB, IFC; \textcolor{camel}{de Mel et al., 2014})
		\end{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (complementary to classical microfinance model)

		\item Structural reasons
		\begin{itemize_2pt}
			\item Women overrepresented in subsistence entrepreneurship
			\item Female entrepreneurs often subject to more severe constraints (e.g., due to household-level reallocation; see, e.g., \textcolor{camel}{Bernhardt et al. 2019}, \textcolor{camel}{de Mel et al., 2009})
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
		\item Example: Final year university course in Tunisia \textcolor{camel}{(Alaref et al., 2020)}
		\begin{itemize_2pt}
			\item Positive impact on business entry tapers off after 4 years
		\end{itemize_2pt}
	\end{itemize_2pt}

High-growth businesses ("gazelles")
\begin{itemize_2pt}
	\item Extensive-margin prediction of future MSE growth is hard \textcolor{camel}{(Fafchamps and Woodruff, 2017)} 
	\begin{itemize_2pt}
		\item Survey, ability measure, expert panel all explain unique variation
		\item But: Business training for predicted gazelles shows no impact
	\end{itemize_2pt}

	\item \citet{McKenzie2017a} finds more encouraging results with a nationwide business plan competition in Nigeria

	\item Small literature on business accelerators and incubators
	\begin{itemize_2pt}
		\item See, e.g., \textcolor{camel}{Cusolito et al., 2020}, \textcolor{camel}{Gonzalez-Uribe et al., 2017}, \textcolor{camel}{Gonzalez-Uribe et al. 2020}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Targeted Training}

Training of specific clusters of practices
\begin{itemize_2pt}	
	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to distinct types of training:

	\begin{enumerate_2pt}
		\item Marketing/sales skills
		\item[]
		\item[]
		\item[]
		\item Finance/accounting skills
		\item[]
		\item[]
		\item[]
	\end{enumerate_2pt}
\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Targeted Training}

Training of specific clusters of practices
\begin{itemize_2pt}	
	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to two distinct trainings:

	\begin{enumerate_2pt}

		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item 61\% increase in profits
			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
		\end{itemize_2pt}

@@

		\begin{itemize_2pt}
			\item "Efficiency focus" on lower costs
			\item 41\% increase in profits
			\item[] $\rightarrow$ Benefits established businesses
		\end{itemize_2pt}

@@

Stylized facts on business consulting
\begin{itemize_2pt}
	\item Three-step procedure
	\begin{enumerate_2pt}
		\item Diagnosing practices
		\item Identifying areas of improvement
		\item Joint and interactive problem solving
	\end{enumerate_2pt}

@@

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %Karlan2015, Bruhn2019
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

@@

Example: Subsidized matching grant program for MSMEs in Mexico \citep{Bruhn2018}
\begin{itemize_2pt}

	\item Weekly 4-hour visits over one year
	\item USD 12,000 per person (subsidized at $70-90\%$)
	\item \textcolor{bdf}{Small positive impacts on profits and ROA after 1 year}

	\item Using admin data, \textcolor{bdf}{57\% higher employment after 5 years}
	\begin{itemize_2pt}
		\item Availability issues of admin data may have introduced selection
		\item Not clear if effects concentrated among few businesses
	\end{itemize_2pt}
\end{itemize_2pt}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=15em]{pics/Bruhn2018_consult.png}
	\label{Bruhn (2018): Consulting}
\end{figure}

@@

\begin{frame}
\frametitle{Multimedia delivery}
TV shows
\begin{itemize_2pt}
	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \textcolor{camel}{(Bjorvatn et al., 2020)} and Egypt \textcolor{camel}{(Barsoum et al., 2018)}
	\item Differential random incentivization schemes
	\item[] $\rightarrow$ No impact on business knowledge and business entry 
	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)

Text messages
\begin{itemize_2pt}
	\item Examples: 
	\begin{itemize_2pt}
		\item Heuristics-based business advice \textcolor{camel}{(Cole and Schoar, 2019)}
		\item Daily personalised inventory level recommendations \textcolor{camel}{(Acimovic et al., 2020)}
	\end{itemize_2pt}
	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
\end{itemize_2pt}
\end{frame}

@@

%\begin{frame}
%\frametitle{Complementary Constraints}
%	\begin{itemize_2pt}
%	\item Core idea: \textcolor{bdf}{Address multiple interrelated constraints}
%	\item Examples: de Mel et al. (2014), Berge et al. (2015), Gine and Iacovone (2021)
%	\end{itemize_2pt}
%\end{frame}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}

Alternative measures of business profits \textcolor{camel}{(de Mel et al., 2009)}
	\begin{itemize_2pt}
		\item 15-16 unannounced visits during one month
		\item Random assignment of profit measure, and accounting diaries, and recall span
	\end{itemize_2pt}

	\begin{enumerate_2pt}
		\item \textcolor{bdf}{Self-reported profits most accurate measure}
		\item[] $\rightarrow$ Correlation with sales-minus-expenditures only $r=0.3$
		\item \textcolor{bdf}{Accounting diaries have no effect on profits} (but on sales)
		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory} 
		\item Entrepreneurs estimate average rival business to \textcolor{bdf}{underreport sales by 30\%}
	\end{enumerate_2pt}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}

Survey media and frequencies {(Garlick et al, 2019)}
\begin{itemize_2pt}
	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.

	\item Random assignment to different survey modes and frequencies
	\begin{enumerate_2pt}
		\item Monthly in-person
		\item Weekly in-person
		\item Weekly phone
	\end{enumerate_2pt}

	\item Survey medium
	\begin{itemize_2pt}
		\item \textcolor{bdf}{All survey modes generally yield similar statistical moments}
		\item Phone surveys yield higher within-firm, cross-temporal variation
		\item[] (Some evidence for greater social desirability bias.)
	\end{itemize_2pt}

	\item Survey frequency
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Higher frequency generally does not alter statistical moments}
		\item No evidence for higher attrition
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

%\begin{frame}
%\frametitle{Variation in Outcome Measures}
%	\begin{itemize_2pt}
%		\item \citep{deMel2009}
%		\item \citep{Bernhardt2019}
%	\end{itemize_2pt}
%\end{frame}

%\begin{frame}
%\frametitle{Self-reports and aggregation}
%	\begin{itemize_2pt}
%	\item Direct measures \citep{deMel2009}
%	\vspace{0.1in}
%	\end{itemize_2pt}
%\end{frame}

@@

\begin{frame}
\frametitle{Variation in Outcome Measures}
Technological aids \textcolor{camel}{(Fafchamps et al., 2012)}
	\begin{itemize_2pt}
	\item Random assignment to Personalized Digital Assistants (PDAs)
	\
	\item Potential channels of impact
	\begin{enumerate_2pt}
		\item More timely data entry
		\item Greater accuracy (especially by correct use of skip patterns)
		\item More and more complex consistency checks

	\item \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
	\item Positive, but limited, effect of consistency checks in reducing variation in firm performance (and within-firm autocorrelation)

@@

	\item Some more obvious constraints:
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Credit constraints} (e.g., Berge et al., 2015, Gin\'e and Iacovone, 2021)
		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
		\item \textcolor{bdf}{Gender norms and constraints}
	\end{itemize_2pt}

@@

	$\rightarrow$ More recent literature highlights additional \textcolor{bdf}{behavioral constraints}

@@

Potential for heuristics and rules of thumb
\begin{itemize_2pt}
	\item Example: Heuristics-based business training program by \citet{Drexler2014}
	\item[] $\rightarrow$ Discussed under \hyperlink{Drexler_thumb}{\beamergotobutton{alternative approaches}}
	\item See also, \textcolor{camel}{Cole and Schoar (2019)} and \textcolor{camel}{Arra\'iz et al. (2019)}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Family and neighborhood}

Family commitments
\begin{itemize_2pt}
	\item \textcolor{bdf}{Unequal responsibilities for child care} (see, e.g., \textcolor{camel}{Delecourt and Fitzpatrick, 2021})
	\begin{itemize_2pt}
		\item Audit study with mystery shoppers among drug stores in Uganda
		\item Average gender profit gap of 60\%
		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
		\begin{itemize_2pt}
			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
			\item .. have \textcolor{bdf}{48\% lower profits}.
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{itemize_2pt}

Market segregation
\begin{itemize_2pt}
	\item Markets can be geographically (and socially) segregated, especially in residential areas
	\begin{itemize_2pt}
		\item Potential \textcolor{bdf}{demand constraints} (in the spirit of \textcolor{camel}{Hardy and Kagy, 2020}, for women in Ghana)
		\item (Scant work, but seems important.)
	\end{itemize_2pt}
\end{itemize_2pt}
\end{frame}

@@

Complementarities in skills
\begin{itemize_2pt}
	\item Clusters of skills may be more valuable in combination
	\begin{itemize_2pt}
		\item Record keeping and financial planning complement each other
	\end{itemize_2pt}
	\item Skills may build on each other
	\begin{itemize_2pt}
		\item Profit calculation relies on record keeping
		\item Advanced inventory management relies on record keeping (and profit calculation)
	\end{itemize_2pt}
\end{itemize_2pt}

@@

Learning styles
\begin{itemize_2pt}
	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
	\begin{itemize_2pt}
		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})
		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Aspirations}

Aspirations theory \citep[following][]{Dalton2016}
\begin{itemize_2pt}
	\item Aspirations are \textcolor{bdf}{desired level of outcome}

	\item In theoretical work, aspirations are modeled as \textcolor{bdf}{reference-dependent preferences}
	\begin{itemize_2pt}
		\item Agent derives utility from relative level wrt their aspirations
		\item[] $\rightarrow$ Aspirations motivate effort
		\item Behavioral constraint: \textcolor{bdf}{Agent neglects outcomes $\rightarrow$ aspirations}
	\end{itemize_2pt}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=12em]{pics/asp.png}
		\label{Aspirations}
	\end{figure}

	\item Consequence: Sufficiently \textcolor{bdf}{poor agent} with sufficiently \textcolor{bdf}{low aspirations} chooses \textcolor{bdf}{suboptimally low effort}
	\item[] $\rightarrow$ Potential for behavioral poverty trap
	\vspace{0.1in}

%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=15em]{pics/Ray2019_aspsMulti.png}
%	\label{Ray(2019): Aspirations}
%\end{figure}

\begin{frame}
\frametitle{Aspirations}

Evidence on aspirations in entrepreneurship
\begin{itemize_2pt}
	\item Descriptive evidence that micro entrepreneurs show \textcolor{bdf}{sizable growth aspirations} \citep{Dalton2018}
	\begin{itemize_2pt}
		\item Both short-term and long-term, for growth in size, labor, and sales
		\item Entrepreneurs update dynamically given new information
	\end{itemize_2pt}

	\item \textcolor{camel}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
		\item Cash also increases aspirations, labor supply, expenditures, and sales
	\end{itemize_2pt}
